Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-09-24 paper/virtual_cytoplasm_v2.tex
discussion

The main difference between the behavior of the macromolecules that compose our model in the crowded system and in the dilute condition is their translational diffusion coefficient, which drops by more around 85\% for the proteins and 93\% for the tRNA (Fig.~\ref{fig:translational_diffusion} A). The slope of a linear regression over values of $D_{cyto}/D_{dil}$ is close to zero ($m = 0.00028$), showing that the drop in diffusion coefficient is independent of the size of the macromolecules. We found that the aggregation of ATP$^{-3}$ and FBP$^{-4}$ around Mg$^{2+}$, which was used as cation for tRNA, leads to its exaggerated confinement. Thus, tRNA is considered as an outlier in our cytoplasm model. In fact, by removing diffusion coefficient of tRNA from the data points of $D_{cyto}/D_{dil}$, the slope of the line changes by 50\% and gets even closer to zero ($m=0.00014$). These results are in agreement with experimental results showing that the translational diffusion coefficient of Green Fluorescent Protein (GFP) in {\em E. coli}, as measured by fluorescence recovery after photobleaching (FRAP), decreased 90\% when compared to {\em in vitro} measurements~\cite{Elowitz1999,Konopka2006}.

@@

Except for some local unfolding for TufA, all crowders were stable during the simulations (Figure \ref{fig:structural_integrity_chain} and their flexibility profile doesn't change significantly (Figure \ref{fig:rmsf}. This shows that our cytoplasm model is stable even in the microsecond range.

\textbf{\color{red}{MISSING RESULTS: WHOLE CROWDER STRUCTURAL INTEGRITY USING BURIED OLIGOMER AREA}}

>>>>

The main difference between the behavior of the macromolecules that compose our model in the crowded system and in the dilute condition is their translational diffusion coefficient, which drops by more around 85\% for the proteins and 93\% for the tRNA (Fig.~\ref{fig:translational_diffusion} A). The slope of the line generated by fitting a linear regression model to values of $D_{cyto}/D_{dil}$ is close to zero (slope $= 0.00028$), showing that the drop in diffusion coefficient is independent of the size of the macromolecules. We found that the aggregation of ATP$^{-3}$ and FBP$^{-4}$ around Mg$^{2+}$, which was used as counter-ion for tRNA, leads to its exaggerated confinement. Thus, tRNA is considered as an outlier in our cytoplasm model. In fact, by removing diffusion coefficient of tRNA from the data, the slope of the linear regression line fitted to $D_{cyto}/D_{dil}$, is reduced by by 50\% and gets even closer to zero (slope $= 0.00014$). These results are in agreement with experimental results showing that the translational diffusion coefficient of Green Fluorescent Protein (GFP) in {\em E. coli}, as measured by fluorescence recovery after photobleaching (FRAP), decreased 90\% when compared to {\em in vitro} measurements~\cite{Elowitz1999,Konopka2006}.

@@

Except for some local unfolding for TufA, all crowders were stable during the simulations (Figure \ref{fig:structural_integrity_chain}) and their flexibility profile doesn't change significantly (Figure \ref{fig:rmsf}) when compared to the dilute condition. This shows that our cytoplasm model is stable even in the microsecond range.
The oligomeric state of the crowders... \textbf{\color{red}{MISSING RESULTS: whole crowder structural integrity using buried oligomer area}}
